Social Participation Ontology: community documentation, enhancements and use examples

### 2017-10-30 plosOne/plosArXiv.tex
minor changes to submit to arXiv

% line numbers
\usepackage[right]{lineno}

@@

% \usepackage{comment}
% \excludecomment{figure}
% \let\endfigure\relax
% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
% Comment the next command to render figures TTM
\renewcommand{\includegraphics}[2][]{\textbf{IMAGE FILE \texttt{\detokenize{#2}}}}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

%% END MACROS SECTION
\usepackage{xr}
\externaldocument{SI/S2ops}
\externaldocument{SI/S3original}
\externaldocument{SI/S4consultation}
\usepackage[section] {placeins}

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
    Participatory democracy advances in virtually all governments and especially in South America
    which exhibits a mixed culture and social predisposition.
    This article presents the ``Social Participation Ontology'' 
    (\ops\ from the Brazilian name \emph{Ontologia de Participa\c{c}\~ao Social})
    implemented in compliance with the Web Ontology Language standard (\owl)
    for fostering social participation, specially in virtual platforms.
    The entities and links of \ops\ were defined based on an extensive collaboration of specialists.
    It is shown that \ops\ is instrumental for information retrieval from the contents of the portal,
    both in terms of the actors (at various levels) as well as mechanisms and activities.
    Significantly, \ops\ is linked to other \owl\ ontologies as an upper ontology
    and via \foaf\ and \bfo\ as higher upper ontologies,
    which yields sound organization and access of knowledge and data.
    In order to illustrate the usefulness of \ops, we present results on ontological expansion
    and integration with other ontologies and data.
    Ongoing work involves further adoption of \ops\ by the official
    Brazilian federal portal for social participation and \ngo s,
    and further linkage to other ontologies for social participation.
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author Summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
%
\linenumbers

@@

An inspection of \vcps\ also yielded a contradiction present in Figure~\ref{fig:diaorig}:
a role cannot execute, initiate or support a cause.
These are done by the social actor.
Therefore, to maintain \vcps\ directions and obtain a sound ontology,
{\tt ops:Role} was removed from \ops.
The result can be seen directly in Figures~\ref{fig:v1} and~\ref{fig:owlCC}.

>>>>

% line numbers
% \usepackage[right]{lineno}

@@

% \usepackage{comment}
% \excludecomment{figure}
% \let\endfigure\relax
% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
% Comment the next command to render figures TTM
% \renewcommand{\includegraphics}[2][]{\textbf{IMAGE FILE \texttt{\detokenize{#2}}}}
% \usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

%% END MACROS SECTION
\usepackage{xr}
\externaldocument{anc/S2ops}
\externaldocument{anc/S3original}
\externaldocument{anc/S4consultation}
\usepackage[section] {placeins}

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Participatory democracy advances in virtually all governments and especially in South America
which exhibits a mixed culture and social predisposition.
This article presents the ``Social Participation Ontology'' 
(OPS from the Brazilian name \emph{Ontologia de Participação Social})
implemented in compliance with the Web Ontology Language standard (OWL)
for fostering social participation, specially in virtual platforms.
The entities and links of OPS were defined based on an extensive collaboration of specialists.
It is shown that OPS is instrumental for information retrieval from the contents of the portal,
both in terms of the actors (at various levels) as well as mechanisms and activities.
Significantly, OPS is linked to other OWL ontologies as an upper ontology
and via FOAF and BFO as higher upper ontologies,
which yields sound organization and access of knowledge and data.
In order to illustrate the usefulness of OPS, we present results on ontological expansion
and integration with other ontologies and data.
Ongoing work involves further adoption of OPS by the official
Brazilian federal portal for social participation and NGO s,
and further linkage to other ontologies for social participation.
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author Summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
%
% \linenumbers

@@

An inspection of \vcps\ reveals a contradiction present in Figure~\ref{fig:diaorig}:
a role cannot execute, initiate or support a cause.
These are done by the social actor.
Therefore, to maintain \vcps\ directions and obtain a sound ontology,
{\tt ops:Role} was removed from \ops.
The result can be seen directly in Figures~\ref{fig:v1} and~\ref{fig:owlCC}.
